When Subgraph Isomorphism is Really Hard, and Why This Matters for Graph Databases\thanks{Part of this paper appeared at IJCAI \citep{DBLP:conf/ijcai/McCreeshPT16}; \cref{section:introduction} has been expanded and \cref{section:models,section:labelled,section:filterverify} are new material.}

### 2017-10-01 paper/paper.tex
kr

    \caption{Behaviour of algorithms on random $k$-regular graphs, as the pattern degree (x-axis)
    and target degree (y-axis) are varied from 0 to $\left|\operatorname{V}\right| - 1$.}
    \label{figure:kr}
\end{figure}

>>>>

    \caption{Behaviour of algorithms on the non-induced problem on random $k$-regular graphs, as the
    pattern degree (x-axis) and target degree (y-axis) are varied from 0 to
    $\left|\operatorname{V}\right| - 1$.}
    \label{figure:kr}
\end{figure}
